Summary stats for paper

### 2021-06-17 analysis/SI_figs.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

---
title: "Figures for paper"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "05/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes our final farms dataset and calculates summary statistics that will be used in the paper.

>>>>

---
title: "Figures for SI"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "06/14/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script takes our final farms dataset and creates the figures which will be showcased in the SI.

### 2021-06-17 analysis/paper_figs.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

This script takes our final farms dataset and calculates summary statistics that will be used in the paper.

@@

test <- all_farms_sf %>%
  filter(country == "United States of America")
mapview(test)

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv")

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("known location \n n = 9,750", "modeled location, known number of farms \n n = 10,519", "modeled locations, estimated number of farms \n n = 75,073"))
    #  geom_vline(xintercept = 135) + # check to make sure it lines up
  #geom_hline(yintercept = 0) # check to make sure it lines up

@@

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## China - near 
chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("D")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
chn_zoom

## Ecuador - Near Guayaquil
ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
ecu_zoom

## Norway
nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms")) +
  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
nor_zoom

# (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none")) + (nor_zoom + theme(legend.position = "none")) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

@@

plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot2
ggsave("analysis/figs/nor_chn_zoom.jpg")

@@

## Radial bar chart of estimation type per country

>>>>

This script takes our final farms dataset and creates the figures which will be showcased in the main manuscript.

@@

test <- all_farms_sf %>%
  filter(country == "United States of America")
mapview(test, zcol = "data_type")

@@

all_farms <- read_csv("all_marine_aquaculture_farms_sources.csv") %>% 
  mutate(data_type_plot = case_when(
    data_type == "modeled location, known number of farms" ~ "Modeled location, known number of farms",
    data_type == "modeled location, estimated number of farms" ~ "Modeled location, estimated number of farms", 
    data_type == "known location" ~ "Known location"
  ))

@@

## create first plot
total_map <- ggplot(data = world) +
  geom_sf(fill = "white", lwd = 0.1) + 
  geom_point(data = all_farms, aes(x = X, y = Y, col = data_type), size = 0.1, alpha = 0.7) +
#  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE, label_axes = list(top = "E", left = "N")) +
  coord_sf(xlim = c(-180, 180), ylim = c(-58, 73), expand = FALSE) +## or could make the latitude distances even i.e. (-72, 72)
  scale_x_continuous(breaks = c(-180, -135, -90, -45, 0, 45, 90, 135, 180), position = "top") +
  scale_y_continuous(breaks = c(-90, -45, 0, 45, 90)) + 
  theme_bw() + 
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
        legend.position = "bottom", 
        legend.title=element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9), nrow=2 )) +
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("known location", "modeled location, known number of farms", "modeled location, estimated number of farms"), labels = c("Known location \n n = 9,750", "Modeled location, known number of farms \n n = 10,519", "Modeled locations, estimated number of farms \n n = 75,073"))
    #  geom_vline(xintercept = 135) + # check to make sure it lines up
  #geom_hline(yintercept = 0) # check to make sure it lines up

@@

chl_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-75, -72.25), ylim = c(-46, -44), expand = FALSE) + # - really good
  # coord_sf(crs = 4326, xlim = c(-75, -72.5), ylim = c(-46, -44), expand = FALSE) +
  theme(legend.position = "bottom", ## put legend on bottom
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("A")  # + 
 #  guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))
chl_zoom

## China - near 
chn_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
#   coord_sf(crs = 4326, xlim = c(120.5, 123), ylim = c(28.5, 30.5), expand = FALSE) + # near Ningbo, in Zhejiang province, near shanghai
  coord_sf(crs = 4326, xlim = c(121.5, 122.75), ylim = c(29.5, 30.5), expand = FALSE) + # part of Zhejiang province
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
        legend.key = element_rect(fill = NA),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("D")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
chn_zoom

## Ecuador - Near Guayaquil
ecu_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
  coord_sf(crs = 4326, xlim = c(-80.5, -79.5), ylim = c(-3.2, -2.2), expand = FALSE) + # part of Guayas province 
  #coord_sf(crs = 4326) + 
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("B")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
ecu_zoom

## Norway
nor_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
    coord_sf(crs = 4326, xlim = c(4, 10), ylim = c(58.5, 61.5), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
nor_zoom

## USA NE 
usa_zoom <- ggplot(all_farms, aes(X,Y, col = data_type_plot)) +
  annotation_map_tile(type = "osm", zoomin = 0) + 
  geom_spatial_point(size = 0.5, alpha = 0.7) + 
  scale_color_manual(values = c("forestgreen", "orange1", "red3"), 
                    breaks = c("Known location", "Modeled location, known number of farms", "Modeled location, estimated number of farms")) +
  # coord_sf(crs = 4326, xlim = c(5, 15), ylim = c(55, 60), expand = FALSE) + ## kattegat and skattergat... not too many farms
    coord_sf(crs = 4326, xlim = c(-123.5, -122), ylim = c(47, 48), expand = FALSE) +
  theme(legend.position = "bottom", 
        legend.title=element_blank(), 
        axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.key = element_rect(fill = NA),
        axis.text.x = element_text(angle = 60, hjust = 1),
panel.border = element_rect(colour = "black", fill=NA, size=3, linetype = "longdash")) +
  ggtitle("C")
  #border(linetype = "longdash")
        #panel.border = element_rect(colour = "black", fill=NA, size=5))
usa_zoom

## Plot with norway instead of USA
# plot1 <- (chl_zoom + plot_layout(guides = "collect") & theme(legend.position = "none") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (ecu_zoom + theme(legend.position = "none"))
# 
# plot1
# ggsave("analysis/figs/chl_ecu_zoom.jpg")
# 
# 
# plot2 <- (nor_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...
# 
# plot2
# ggsave("analysis/figs/nor_chn_zoom.jpg")

## we saved both of those images separately. Then we export them to google drawings, and combine together. Once combined, reupload to figs folder as "zoom_fig_final_nor.jpg"

## Plot with USA instead of norway

@@

plot2 <- (usa_zoom +  plot_layout(guides = "collect") & theme(legend.position = "bottom") & guides(color = guide_legend(override.aes = list(size = 3, alpha = 0.9, fill = NA)))) + (chn_zoom + theme(legend.position = "none")) ## save this output in the plot window...

plot2
ggsave("analysis/figs/usa_chn_zoom.jpg")

@@

ARCHIVE: Radial bar chart of estimation type per country

### 2021-06-17 analysis/paper_stats.Rmd
ran 3 different versions of the mapping. 10km, 35km, and 45km from ports

# test <- all_farms_sf %>%
#   filter(iso3c == "USA")
# mapview(test)
```

@@

# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of the total estimated points, and only had 15 known location points

chn_data_estimated <- all_farms %>%
  filter(iso3c == "CHN") %>%
  filter(data_type == "modeled location, estimated number of farms")
# 58151 points
58151/75073 # 0.7745927 = 77%

>>>>

# test <- all_farms_sf %>%
#   filter(iso3c == "USA")
# mapview(test)

@@

# Some of the world’s largest aquaculture producers had a noticeable paucity of aquaculture location data, particularly China, whose represented 77% of all points, and only had 15 known location points

chn_data_estimated <- all_farms %>%
  filter(iso3c == "CHN") #%>%
  #filter(data_type == "modeled location, estimated number of farms")
# 58166 points
58151/95342 # 0.6099201 = 61%
